Blockchain System

### 2021-01-04 papers/execution-model/model.tex
after monday meeting

 \begin{definition}%[Pending operation]
An \emph{operation} is represented by a tuple  $\langle  \OP, \TIME, \STATUS
\rangle $, where $\OP$ is an operation, $\TIME$ is the time when the
operation was injected, and $\STATUS$ is either $\STATUSPENDING$,
$\STATUSINCLUDING\ \TIME'$, or $\STATUSTIMEOUT$.  
\end{definition}
\begin{definition}
  The pool of operations is defined as a partial mapping from
  operation hashes $\OPH$:
  \begin{align*}
    \PENDING &= \TOPH \partialto \TOP\times \TTIME \times \TSTATUS \\
    \TSTATUS&= (\STATUSPENDING + \STATUSINCLUDED\ \TTIME + \STATUSTIMEOUT)
  \end{align*}

  A pool $\PENDING$ is \emph{well-formed} if, for all $\OPH$, if $\PENDING (\OPH) =
  \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$, 
  then $\TIME' > \TIME$.
\end{definition}

A \emph{pending operation} is represented by
$\langle  \OP, \TIME, \STATUSPENDING\rangle $,
where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected.
Once it is accepted, it changes to an \emph{accepted operation}:
$\langle  \OP, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
$\TIME'> \TIME$ is  when the operation was included in the
blockchain.  The operation can also be dropped at any time, which is
represented by
$\langle  \OP, \TIME, \STATUSTIMEOUT\rangle $. There are several
causes for dropping, primarily timeout or overflow of the pending
pool which is limited in size in the implementation.

@@

\begin{definition}%[Blockchain]
  The \emph{state of a blockchain} is a tuple
  $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]$ where
  $\PENDING$ is a pool of operations, $\MANAGERS$ is a map of managers,
  $\CONTRACTORS$ is a map of contractors, and $\TIME$ is the current
  time. 
\end{definition}

Properties of blockchain state transitions

If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
[\PENDING', \MANAGERS', \CONTRACTORS', \TIME']$, then
\begin{itemize}
\item $\TIME \le \TIME'$
\item $\DOM (\PENDING) \subseteq \DOM(\PENDING')$
\item for all $\OPH \in \DOM(P)$, if  $\PENDING (\OPH) = \Angle{\OP,
    \TIME, \STATUS}$, then either
  \begin{itemize}
  \item     $\PENDING'    (\OPH) = \PENDING (\OPH)$; or
  \item $\STATUS  = \STATUSPENDING$ and $\PENDING' (\OPH) =
    \Angle{\OP, \TIME, \STATUSTIMEOUT}$; or
  \item  $\STATUS  = \STATUSPENDING$, $\BLOCKCHAIN'.\TIME - \TIME
    \le 60 $, and
    $\PENDING' (\OPH) =       \Angle{\OP, \TIME, \STATUSINCLUDED\
      \BLOCKCHAIN.\TIME}$.
  \end{itemize}

 \item $ \DOM (\MANAGERS) \subseteq \DOM (\MANAGERS')$
 \item for all $\PUK \in \DOM (\MANAGERS)$ if $\MANAGERS (\PUK) =
   \Angle{\BAL, \COU}$ where $\COU = (n, b)$
   \begin{itemize}
   \item if $b= \FALSE$, then $n' = n$
   \item if $b= \TRUE$ and $b'=\TRUE$, then $n' =n$
   \item if $b=\TRUE$ and $b'=\FALSE$, then $n' \in \{ n,  n+1\}$
   \end{itemize}

 \item $ \DOM (\CONTRACTORS) \subseteq \DOM (\CONTRACTORS')$

>>>>

 \begin{definition}%[Pending operation]
An \emph{operation} is represented by a tuple  $\langle  \OP, \TIME, \STATUS
\rangle $, where $\OP$ is an operation, $\TIME$ is the time when the
operation was injected, and $\STATUS$ is either $\STATUSPENDING$,
$\STATUSINCLUDED\ \TIME'$, or $\STATUSTIMEOUT$.  
\end{definition}
\begin{definition}
  The pool of operations is defined as a partial mapping from
  operation hashes $\OPH$:
  \begin{align*}
    \PENDING &= \TOPH \partialto \TOP\times \TTIME \times \TSTATUS \\
    \TSTATUS&= (\STATUSPENDING + \STATUSINCLUDED\ \TTIME + \STATUSTIMEOUT)
  \end{align*}

  A pool $\PENDING$ is \emph{well-formed} if, for all $\OPH$, if $\PENDING (\OPH) =
  \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$, 
  then $\TIME' \ge \TIME$.
\end{definition}

A \emph{pending operation} is represented by
$\langle  \OP, \TIME, \STATUSPENDING\rangle $,
where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected.
Once it is accepted, it changes to an \emph{accepted operation}:
$\langle  \OP, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
$\TIME' \ge \TIME$ is  when the operation was included in the
blockchain.  The operation can also be dropped at any time, which is
represented by
$\langle  \OP, \TIME, \STATUSTIMEOUT\rangle $. There are several
causes for dropping, primarily timeout or overflow of the pending
pool which is limited in size in the implementation.

@@

\begin{definition}%[Blockchain]
  The \emph{state of a blockchain} is a tuple
  $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]$ where
  $\PENDING$ is a pool of operations, $\MANAGERS$ is a map of managers,
  $\CONTRACTORS$ is a map of contractors, and $\TIME$ is the current
  time. 
\end{definition}
\clearpage{}
\subsection{Properties of blockchain state transitions}

If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
[\PENDING', \MANAGERS', \CONTRACTORS', \TIME']$, then
\begin{itemize}
\item $\TIME \le \TIME'$
\item $\DOM (\PENDING) \subseteq \DOM(\PENDING')$
\item for all $\OPH \in \DOM(P)$, if 
  $\PENDING (\OPH) = \Angle{\OP,  \hat\TIME, \STATUS}$, then either
  \begin{itemize}
  \item     $\PENDING'    (\OPH) = \PENDING (\OPH)$; or
  \item $\STATUS  = \STATUSPENDING$ and $\PENDING' (\OPH) =
    \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}$; or
  \item  $\STATUS  = \STATUSPENDING$, $\TIME - \hat\TIME
    \le 60 $, and
    $\PENDING' (\OPH) =       \Angle{\OP, \hat\TIME, \STATUSINCLUDED\
      \TIME}$.
  \end{itemize}

 \item $ \DOM (\MANAGERS) \subseteq \DOM (\MANAGERS')$
 \item for all $\PUK \in \DOM (\MANAGERS)$\\
   if $\MANAGERS (\PUK) =
   \Angle{\BAL, \COU}$, 
   then $\MANAGERS' (\PUK) =
   \Angle{\BAL', \COU'}$ and
   \begin{itemize}
   \item if $\COU.b=\TRUE$ and $\COU'.b=\FALSE$, then $\COU.n' \in \{
     \COU.n,  \COU.n+1\}$,
   \item otherwise $\COU.n = \COU'.n$
   \item If $\COU.n = \COU'.n$, then $\BAL = \BAL'$.
   % \item if $\COU.b= \FALSE$, then $n' = n$
   % \item if $\COU.b= \TRUE$ and $b'=\TRUE$, then $n' =n$
   \end{itemize}

 \item $ \DOM (\CONTRACTORS) \subseteq \DOM (\CONTRACTORS')$
   \todo{say something about contract state}
\end{itemize}
